---
title: "Test"
author: "Giang"
date: "6/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, f2c}
F2C <- function(x) {
  <<check-arg>>
  <<convert>>
}
```

First, we check if the input value is numeric:

```{r, check-arg, eval=FALSE}
  if (!is.numeric(x)) stop("The input must be numeric!")
```

Then we do the actual conversion:

```{r, convert, eval=FALSE}
  (x - 32) * 5/ 9
```

```{r}

F2C(370)

```

Here is a code chunk that is not evaluated:

```{r, chunk-one, eval=FALSE}
1 + 1
2 + 2
```

Now we actually evaluate it:

```{r, chunk-one, eval=TRUE}
```

Possible to reuse chucks. First one is not running. Second one is.
But avoid this as save files might be replaced.

```{r chunk-a, ref.label=c('chunk-c', 'chunk-b')}
```

```{r chunk-b}
# this is the chunk b
1 + 1
```

```{r chunk-c}
# this is the chunk c
2 + 2
```
In other words, chunk-a is essentially this:


```{r chunk-a}
# this is the chunk c
2 + 2
# this is the chunk b
1 + 1
```

The chunk option ref.label takes a vector of chunk labels to retrieve the content of these chunks. This is a very flexible way of reorganizing code chunks in a document without resorting to cut-and-paste. It does not matter if the code chunks referenced are before or after the code chunk that uses ref.label. An early code chunk can reference a later chunk.
